Viscous Erosion in Porous Media

### 2018-02-18 docs/methods/erosion_methods.tex
Writing up the simpler time-stepping rule in the methods paper.
NM

With the shear stress computed, we are now ready to evolve the interface
of each body using equations~\eqref{eqn:Levo1}
and~\eqref{eqn:thetaevo1}. As described in Section~\ref{sec:thetaL}, we
use the {\thL} framework, with $\theta$ being the tangent angle and $L$
the total arc length of a given boundary, and with the boundaries
parameterized by normalized arc length $\alpha = 2 \pi s / L$.

@@

Next, at the second stage of RK2, we discretize as
\begin{align*}
\frac{L^{(n+1)} - L^{(n)}}{\Dt} &= \Mterm^{(n+1/2)}, \\
\frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} &=
\mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}.
\end{align*}
We again compute the integrating factor, $\mu_k^{(n+1)}$ via the
\todo[inline]{insert integration rule}, giving
\begin{align*}
\thhat_k^{(n+1)} = 
& \thhat_k^{(n)}
\exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
& \Dt \, \hat{\NLterm}_k^{(n+1/2)}
\exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} -
\elfun^{(n)} \right) \right).
\end{align*}

>>>>

With the shear stress computed, we are now ready to evolve the interface
of each body using equations~\eqref{eqn:Levo1}
and~\eqref{eqn:thetaevo1}. As described in Section~\ref{sec:thetaL}, we
use the {\thL} framework, with $\theta$ being the tangent angle and $L$
the total arc length of a given boundary. Each boundary is
parameterized by normalized arc length $\alpha = 2 \pi s / L$.

@@

Next, at the second stage of RK2, we discretize as
\begin{align*}
\frac{L^{(n+1)} - L^{(n)}}{\Dt} &= \Mterm^{(n+1/2)}, \\
\frac{ \mu_k^{(n+1)} \thhat_k^{(n+1)} - \thhat_k^{(n)}}{\Dt} &=
\mu_k^{(n+1/2)} \hat{\NLterm}_k^{(n+1/2)}.
\end{align*}

We compute the integrating factor with RK2 to get
\begin{align}
\thhat_k^{(n+1)} = & \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
& \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{2} \eps k^2 \Dt \left( 2 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
\end{align}

%We again compute the integrating factor, $\mu_k^{(n+1)}$ via the
%\todo[inline]{insert integration rule}, giving
%\begin{align*}
%\thhat_k^{(n+1)} = & \thhat_k^{(n)} \exp \left( - \epsilon k^2 \Dt \elfun^{(n+1/2)} \right) +  \\
%& \Dt \, \hat{\NLterm}_k^{(n+1/2)} \exp \left( - \frac{1}{4} \eps k^2 \Dt \left( 3 \elfun^{(n+1/2)} - \elfun^{(n)} \right) \right).
%\end{align*}
